Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-05 ongoing/report/sec_1_introduction.tex
Split files

\documentclass[12pt]{article}

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[linkcolor=blue]{hyperref}
\usepackage{xcolor}
\usepackage[ocgcolorlinks]{ocgx2}
\usepackage{stackengine}

\author{Tzu-Yu Jeng}
\date{\today}

\title{Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound}

\newcommand{\MB}[1]{\mathbb{#1}}
\newcommand{\MC}[1]{\mathcal{#1}}
\newcommand{\MF}[1]{\mathfrak{#1}}
\newcommand{\RM}[1]{\mathrm{#1}}
\newcommand{\V}[1]{\stackunder[1.2pt]{$#1$}{\rule{.9ex}{.075ex}}}
\newcommand{\M}[1]{\V{\V{#1}}}
\newcommand{\T}[1]{\tilde{#1}}
\newcommand{\IP}[1]{\langle #1 \rangle}

\renewcommand{\H}{\dagger}

\newcounter{NumResult}
\newcommand{\myCount}
{
   \stepcounter{NumResult}
   \textbf{\arabic{NumResult}}
}

\newcommand {\Result} [2]
{
   \bigskip
   \myCount \textbf{#1} \par
   {#2} \par
   \hfill \(\blacksquare\)
   \bigskip
}

\begin{document}

\maketitle

\section{Acknowledgement}

\section{Abstract}

Multiple-input-multiple-output (MIMO) communication is widely expected to be the next-generation wireless communication scheme.
However, reliable communication in such r\`egime usually requires that the channel response be known at the receiver, necessary for example in beamforming algorithm and channel calibrupation.
It is then a non-trivial problem to estimate real-world wireless channels.

Meanwhile, in the millimeter wave r\`egime, which is usually used in tandem with MIMO, channel often exhibits sparse properties.
If the sparsity is exploited, few observations may suffice to estimate the channel, and such algorithm falls under the study of compressive sensing, an active area that has recently emerged.
A promiment estimator is The Dantzig Selector (DS) proposed by Tao and Cand\'es, and it is DS which was first applied in channel estimation context.
However, Orthogonal Matching Pursuit (OMP) later emerges as a low-complexity solution, and following-up literature usually used OMP rather than DS as a result.

In this article, we utilize a hybrid structure at both transmitter and receiver end, each of them having both digital and analog percoders and combiners.
We argue in favor of DS, and verify that DS is, as originally perceived, ideal in certain senses.
DS encompasses a more general setting than OMP, such as in its requirement of restricted isometry property (RIP) only, and as in its allowance of noise corruption.
Moreover, we extend their proof to derive a stronger bound in the setting of estimation of millimeter wave channel for almost-sparse channel matrix

We show explicitly that DS may be cast as a second order cone problem (SOCP), and primal-dual technique is ready to be used.
Simulation is done with both DS and OMP, and we discuss their respective merits as our conclusion.

\section{Introduction}

@@

We restrict our discussion to the Hilbert space over the field of \(\MB{R}\) or \(\MB{C}\), equipped with usual inner product, here the complex numbers has natural interpretation as the phasor of electronic waves.
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
To avoid being too pedantic, we simply write \(\V{a} \in \MB{C}^N\) to stress \(\V{a}\) is a \(N\)-dimensional vector, and the role it plays in the vector space is understood.
Similarly, we also write \(\V{A} \in \MB{M}(M,N)\) to stress \(\V{A}\) is a \(M\) by \(N\) matrix, and the role it plays as linear transformation is understood.
Inner product is denoted as \(\IP{ \MB{a}, \MB{b} }\).
Slightly abusing notation, denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Especially, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).

\(|a|\) denotes the magnitude for real or complex numbers.
\(\|\V{a}\|_p\) denotes the \(\ell_\infty\)-norm of \(\V{a}\).
Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.
The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(\MF{Re}(a) +i \MF{Im}(a)\)

Denote as \(\MB{P}(X)\) the probability, \(\MB{E}(X)\) the expectation, \(\MB{Var}(X)\) the variance.
Since our discussion involving the entire communication system will get very complicated, we shall add subscripts on probabilistic integrals, including \(\MB{P}\) and \(\MB{E}\).

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
The capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information (CSI) is well-known, as was first proved by Teletar, to be roughly in the form \(\log \det (I +\RM{SNR})\).
But that knowledge is hardly always available.
What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-CSI expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).

Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithm also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus in need.

\subsection{Recovery of Sparse Vector in the Noiseless Case}

It is a recent developemnt that the estimation of channels is facilitated by advances of compressed sensing.
A series of paper by Cand\`es and Tao (2006) marks its advent.
The idea is that, in many important statsitical applications, the number of variables or parameters \(p\) is much larger than the number of observations \(n\).
In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?
Of course, more assumption must be made to make the question meaningful.
Cand\`es and Tao's pioneering work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.
They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.

They showed that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.

\Result
{Definition}
{
\(x \in \MB{K}^N\) is called \(s\)-sparse, if
\begin{gather} 
\# \RM{supp}(x) \leq s
\end{gather}
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\RM{min}_{x' \in \MB{R}^K}
\quad \|x'\|_1
\quad \RM{s.t.} \quad A x' =y
\end{gather}
}

\Result
{Theorem}
{
Let \(y =Ax\).
Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
\begin{gather}
\delta_{S} +\delta_{2S} +\delta_{3S} <1
\end{gather}
}

\Result
{Definition}.
{
Let \(A\) be an \(n \times p\) matrix having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
\begin{gather}
(1-\delta_S) \|x\|^2
\leq \|A_T x\|_2^2
\leq (1+\delta_S) \|x\|^2
\end{gather}
}

@@

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
\begin{gather}
| \IP{ X_T c, X_{T'} c' } |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
\end{gather}

Later Cand\`es and Tao  obtained a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006, which will be a main reference of this article), with a convex program called The Dantzig Selector they proposed (hencefore DS), they can recover the noisy case too.
They argues in their work that DS has many advantages, and the error probability is upper bounded quantatively and shown to be vanishingly small.
From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

For concreteness, consider a liear transformation with noise,
\begin{gather}
y =Ax +z
\end{gather}
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
\begin{gather}
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \notag
\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
\end{gather}
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \MB{V}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
\begin{gather}
   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp(-n c_0(\epsilon))
\end{gather}
where we have
\begin{gather}
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
\end{gather}
}

@@

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
\begin{gather}
y[t] =(x[t] \star h[t]) +z[t]
\end{gather}
where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
\begin{gather}
y =X h
\end{gather}
where \(X\) takes the form
\begin{align}
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
\end{align}
We seek to get \(h\) in this undertermined system.

@@

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \MB{V}(M)\), \(x \in \MB{V}(N)\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

@@

\Result
{Theorem}
{
   Following the setting described above, suppose, for \(0 <\delta <1\),
\begin{gather}
   M \geq 16s \log (N/\delta)
\end{gather}
Then   Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
}

@@

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
\begin{gather}
   \V{y} =\M{W} \M{H} \M{F} \V{x}
\end{gather}

\Result
{Definition}
{
Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}(n,m)\).
}

\Result
{Definition.}
{
For \(\RM{vec}(A) \in \MB{M}(n,m)\) and \(\RM{vec}(A) \in \MB{M}(n,m)\)
Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
}

With (), scholars often exploit the relation
\begin{gather}
\RM{vec}(Y)
=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
\end{gather}

@@

\subsection{Further development on CSS}

The literature on CSS has since been vast, and we need not and cannot go through all of them here.
Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.

@@

\section{Problem Setting}

\subsection{Channel Model}

Since expression involving probability will get very complecated, introduce the direct product
\begin{gather}
\Omega
=\Omega_t \times \Omega_h \times \Omega_n \times \Omega_r
\end{gather}
to denote the overall sample space, where

\begin{itemize}
\item \(\Omega_t\) denotes the collection of probability samples at the transmitter end,
\item \(\Omega_h\) denotes that of the communication channel,
\item \(\Omega_h\) denotes that of the noise arising in the communication channel,
\item \(\Omega_r\) denotes that at the receiver end.
\end{itemize}
%
\(\omega_1\) stands for the event space index of the transmitter end, and \(\omega_2\) for the channel, and \(\omega_3\) for the receiver.

We restrict our consideration to the uniform linear array, which can be modeled as
\begin{gather}
\V{a} \in \MB{V}(N_h) \\
\V{a}(\psi')
=\sum_{n=1}^{N} \RM{e}^{n \psi' i} \V{u}_n
\end{gather}
where \(i\) is the imaginary unit, \(\V{u}_n\) is the unit vector of the \(n\)-th component.

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}\big( \frac{d}{\lambda} \sin \varphi_l' \big) \V{a}\big( \frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l' \big)^\H
\end{gather}
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
\begin{gather}
\varphi_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \varphi_l' \\
\vartheta_l
=\frac{d_{\RM{arr}}}{\lambda} \sin \vartheta_l'
\end{gather}
to get a simpler form
\begin{gather}
H
=\sum_{l=0}^L \alpha_l \V{a}(\varphi_l) \V{a}(\vartheta_l)^\H
\end{gather}

\Result
{Definition.}
{
}

\subsection{System Model}

We consider the situation with a hybrid structure at both transmitter and receiver end.
Each end consists of both digital and analog percoders and combiners.
In the transmitter end, there are digital precoder \(F_B\) and analog precoder \(F_R\).
Similarly, in the receiver end, there are digital combiner \(W_B\) and analog combiner \(W_R\).
To set up notation, we list them as below.
\begin{gather}
F_B \in \MB{C}^{N_r \cdot N_y} \\
F_R \in \MB{C}^{N_h \cdot N_r} \\
F_B \in \MB{C}^{N_r \cdot N_h} \\
F_B \in \MB{C}^{N_y \cdot N_r}.
\end{gather}
Recall that analog precoder is restricted to have value with magnitude being unity.
\begin{gather}
 |F_R(n_1,n_2)| =1, \quad
 n_1 =1, \dotsc N_h, \quad
n_2 =1, \dotsc N_r \\
 |W_R(n_1,n_2)| =1, \quad
 n_1 =1, \dotsc N_r, \quad
n_2 =1, \dotsc N_h
\end{gather}

And we consider zero-mean, unity-variance additive white Gaussian noise \(z\).
Since we restrict our discussion to a specific slice of time, the signal \(z\) degrades as a entrywise i.i.d.\ standard normal distribution vector.

In summary, the effective channel may be written as
\begin{gather}
Y (\omega_h, \omega_e)
:=W_B(\omega_r) W_R(\omega_r) ( H(\omega_h) F_R(\omega_t) F_B(\omega_t) +Z(\omega_z) )
\end{gather}
Supress the event space index for brevity, we restate the same equation as
\begin{gather}
Y
:=W_B W_R ( H F_R F_B +z )
\end{gather}

\subsection{Proposed Method}

The effective channel \(\M{Y}\) has \(N_y\) columns, but to estimate it, we may agree to send one pilot signal, which is one of the standard basis, at a time, namely \(\V{u}_n\).
This way, we may denote the acquired effective channel matrix \(\M{Y}\) under noisy observation as (borrowing Matlab's colon notation to denote columns)
\begin{gather}
\M{Y}(:,n)
:=\M{W}_B \M{W}_R ( \M{H} \M{F}_R \M{F}_B \V{u}_{n_y} +\V{z} ), \quad
n_y =1, 2, \dotsc, N_y
\end{gather}
The crux of the matter is the recovery of \(\M{H}\) with knowledge of \(\M{Y}\), and of course \(\M{W}_R, \M{W}_B, \M{F}_R, \M{F}_B\) which are in our control.

Following previous work on CSS, we write
\begin{gather}
\V{h} := \RM{vec}(\M{H}) \\
\V{y} := \RM{vec}(\M{Y}) \\
\M{P}' :=(\M{F}_R \M{F}_B) \otimes (\M{W}_B \M{W}_R)
\end{gather}
to formulate our goal as sparse recovery problem of \(\RM{vec}(H)\) to be
\begin{gather}
\V{y} =\M{P}' \V{h} +\V{z}
\end{gather}
But, as we have motivated in previous sections, we want to elimitate the angle grid quantization problem, and we want to use DS by considering sparse vector.
What shall we do?

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
\begin{gather}
\M{K} \in \MB{M}(N_h, N_h) \\
\M{K}(n_1, n_2) =\frac{1}{\sqrt{N}} \RM{e}^{2\pi i n_1 n_2 /N},
\quad n_1, n_2 =0,1,2,\dotsc, N-1
\end{gather}
where \(i =\sqrt{-1}\).
And observe that, if we write
\begin{gather}
\M{G}
=\M{K}^\H \M{H}
\end{gather}
which has the interpretation as the spatial frequency domain representation of \(\M{H}\), then
\begin{gather}
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
\end{gather}
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.
To the best of our knowledge, no work has explicitly considered the beamspace CSS.

That is to say, \(\M{K}^\H \V{z}\) may be absorbed, and a similar Kronecker product may be used.
\begin{gather}
\RM{vec}(\M{Y})
\approx \big[ (\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K}) \big] \RM{vec}(\M{H})
\end{gather}
To simplify notation, set 
\begin{gather}
\M{P} =(\M{F}_B^\H \M{F}_R^\H) \otimes (\M{W}_B \M{W}_R \M{K})
\end{gather}
The instances of \(\M{P}\) is completely determined in the transmitter and receiver end, that is
\begin{gather}
\M{P} =\M{P}(\omega_t, \omega_r)
\end{gather}
If so, our program reads

\Result
{Program}
{
Let \(\M{H}(\omega_h, \omega_n)\) be the virtual channel, and \(\M{W}_R(\omega_r)\) the random analog combiner, \(\M{W}_B(\omega_r)\) the random analog combiner, \(\M{F}_R(\omega_t)\) the random analog combiner, \(\M{F}_B(\omega_t)\) the random analog combiner, and \(K\) the discrete Fourier matrix, all as described in previous sections.
Suppose \(\M{Y}\) is the acquired effective channel matrix under corruption of noise \(\V{z}\).
\(\M{P}\) is defined just above in ().
Then, with parameter \(\gamma\) specified, define the following program
\begin{gather}
\hat{\V{g}}
=\underset {\V{h}} {\RM{min}} \|\V{h}\|_1 \quad
\RM{s.t.}\quad \|P^\H (y -P h)\|_\infty \leq \gamma
\end{gather}
And convert \(\hat{g}\) back to the space domain as
\begin{gather}
\hat{h}
=K \hat{g}.
\end{gather}
And finally recover the estimated \(H\) as
\begin{gather}
\hat{H} =\RM{vec}^{-1} (\hat{h})
\end{gather}
}

It, then, will not be hard to establish Cand\`es and Tao's result to the setting of millimeter wave virtual channel, and resulting bound is immediate under straighforward work, as follows.

\section{Results and Proofs}

We follow the argument outlined in ``The Dantzig Selector'' and fill the content.
The sparse vector to be recovered of our investigation is \(g \in \MB{C}^{N_h^2}\), and we continue to use \(\hat{g}\) to denote the Dantzig Selector.

We first establish a technical lemma that shows \(\RM{supp}(g)\) has roughly cardinal \(L\).
At the heart of the argument, the lemma provides the basis on which \(g\) is almost-sparse.

Consider
\begin{gather}
d =g -\hat{g}
\end{gather}
And let
\begin{itemize}
\item \(\MC{A}\) be the largest \(L\) position of \(g\).
\item \(\MC{B}\) be the largest \(L\) position of \(d\) except on \(\MC{A}\).
\item \(\MC{C} =\{1, \dotsc, N_h^2\} -( \MC{B} \cup \MC{C} )\), i.e., the complementary index set.
\end{itemize}
So \(\MC{A}, \MC{B}, \MC{C}\) are mutually exclusive index sets by construction:
\begin{gather}
\MC{A}, \MC{B}, \MC{C} \subset \{1, \dotsc, N_h^2\} \\
\MC{A} \cap \MC{B} =\MC{B} \cap \MC{C} =\MC{A} \cap \MC{C} =\varnothing \\
\MC{A} \cup \MC{B} \cup \MC{C} =\{1, \dotsc, N\}.
\end{gather}

\Result
{Notation}
{
Let \(T \subset \MB{N}\).
Denote as \(X_T\) the columns of \(X\) having indices in \(T\).
}

>>>>

@@

\(|a|\) denotes the magnitude for real or complex numbers \(a\).
The real and imaginary part of \(a\) will be denoted respectively as \(\MF{Re}(a)\) and \(\MF{Im}(a)\), respectively, thus \(a =\MF{Re}(a) +i \MF{Im}(a)\)

We restrict our discussion to \(\MB{R}^N\) or \(\MB{C}^N\) seen as the Hilbert space , equipped with standard inner product.
Lower case Latin alphabets with single underline, like \(\V{a}\), denote vectors, and upper case Latin alphabets with double underlines, like \(\M{A}\), denote matrices.
Particularly, define \(\V{1} =\IP{ 1, \dotsc, 1 }\) and \(\V{1} =\IP{ 1, \dotsc, 1 }\).

In our context, the complex numbers has natural interpretation as the phasor of electronic waves.
Of course, scalar operation on \(\MB{R}^N\) is over field \(\MB{R}\), and that on \(\MB{C}^N\) is over field \(\MB{C}\).
We use \(\MB{K}\) to refer to either \(\MB{R}\) or \(\MB{C}\).
Not to avoid confusion, we call the Hilbert space \(\MB{K}^N\) over \(\MB{K}\) to be \(\MB{V}_{\MB{K}} (N)\).
We also call the collection of \(M\) by \(N\) matrices to be \(\MB{M}_{\MB{K}}(M,N)\), and its role as linear transformation is understood.
Inner product of \(\V{a}\) and \(\V{b}\) is denoted as \(\IP{ \V{a}, \V{b} }\).
Slightly abusing notation, we denote as \(\V{a}(n)\) the \(n\)-th component of \(\V{a}\), and denote as \(\V{A}(m,n)\) the \((m,n)\)-entry of \(\V{A}\)
Particularly, \(\V{u}_n\) is the \(n\)-th unit vector in the Cartesian coordinates (not to be confused with the noise).
\(\|\V{a}\|_p\) denotes the \(\ell_p\)-norm of vector \(\V{a}\).
Recall that \(\ell_\infty\)-norm is the maximum-magnitude norm.

Denote as \(\MB{P}(X)\) the probability, and \(\MB{E}(X)\) the expectation.
Since our discussion involving the entire communication system will get very complicated, we may spell out the dependence of event space index on random variables.

@@

The figure of merit of a MIMO system is usually considered to be the channel capacity.
In vague terms, the capacity \(C\) of a MIMO channel \(\M{H}\) at perfect channel state information is well-known to be roughly in the form \(\log \det (I +\RM{SNR})\), but that knowledge is hardly always available.
What makes things more difficult is the case that \(\M{H}\) is determined from not only the noise itself, but also inherent parameter --- such as, in our case, as shall be seen, the angle of departure and arrival.
It is pointed out that the capacity written in explicit dependence of such parameters is a difficult and long-standing problem (Goldsmith et.\ al.\ 2003).
Nevertheless, the perfect-channel-state-information expression of channel capacity is often used regardless of these issues.
Indeed, analysis of precoding algorithm, for example, usually makes use of the sum rate \(\log \det (I +\RM{SNR})\).

Therefore the real-time estimation, \(\hat{\M{H}}\), of \(\M{H}\) is of paramount importance.
Needless to say, when the \(\hat{\M{H}}\) is imprecise, resulting analysis is also undermined.
With more antennae present, conventional training-based algorithms also increase in complexity and storage.
In real applications, channel may also be fast varying with respect to time, and a high complexity algorithm is surely less than being ideal.
A design of new algorithms that addressed these issues is thus necessary.

It is a recent developement that the estimation of channels is facilitated by advances of compressed sensing.
A series of paper by Cand\`es and Tao (2006) marks its advent.

To motivate their work, note that it is a common situation in statsitical applications that the number of model parameters \(N_p\) is much larger than the number of observations \(N_o\).
Here, we consider
\Disp{
N_p \gg N_o
}

In such case of insufficient observations, possibly even with noise, do we have the knowledge of all \(p\) variables?

Of course, more assumption must be made to make the question meaningful.
They showed frst that that in the noiseless case (Cand\`es and Tao 2006,``Decoding by Linear Programming''), it is possible to recover the sparse signal, under a \(\ell_1\)-1 minimization program.
The work reveals the phenomenon that few observations of the signal in question may be sufficient for us to resonstruct the signal when it is sparse in a certain sense.

Later they established a stronger result that (``The Dantzig Selector'' Cand\`es and Tao 2006), with another \(\ell_1\)-1 minimization program they named The Dantzig Selector (hencefore DS), they can recover the noisy case too.
They argue that such recovery of signals is possible, if we make a few carefully constructed, and seemingly random measurements.
Ever since, it becomes feasible that a camera equipped with few sensors may obtain high quality images, greatly reducing the subsequent cost.
In addition, they derived a probability bound of mean suqare error, showing the probability of successful recovery is overwhelming.

From the realistic perspective, DS formulates the sparse sensing problem as an \(\ell_2\) minimization problem, which is convex, thus techniques from convex optimization may readily be used.
Indeed, they have put the code on the web for the reader to access and verify (Cand\`es \& Romberg 2005).

In this article we focuss on DS, and we introduce several notions before we describe their wok.
To facilitate reader's understanding, in this section we will consistently use \(N_s\) and \(N_s\) to denote matrix dimensions.
Following Cand\`es and Tao, we borrow the term ``support'' from the context of analysis, where it denotes the set on which a function is nonzero.

\Result
{Definition}
{
We say \(T (N) =\{1, \dotsc, N\}\), \(N \in \MB{N}\) is the support of vector space \(\MB{V}_{\MB{K}} (N)\).
}

\Result
{Definition}
{
Suppose \(\M{A} \in \MB{M}_{\MB{K}} (N_1, N_2)\).
Let \(\MC{T} \subset T (N_2)\).
Denote as \(\M{A}_{\MC{T}}\) the columns of \(\M{A}\) having indices in \(\MC{T}\).
}

\Result
{Definition}
{
\(x \in \MB{V}_{\MB{K}} (N)\) is called \(s\)-sparse with support \(\MC{A}\), \(s \in \MB{N}\), if there is \(\MC{A} \subset T (N)\) such that
%
\Disp{ 
x_{T (N) -\MC{A}} =\V{0}
}
with
\Disp{ 
\# \MC{A} \leq s.
}
%
That is, only at most \(s\) components of vector \(x\) is nonzero.
}

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
%
\Disp{
\min_{x' \in \MB{V}_\MB{K}(K)}
\quad \|x'\|_1
\quad \RM{s.t.} \quad A x' =y
}
%
}

\Result
{Theorem}
{
Let \(y =Ax\).
Suppose \(x\) is \(s\)-sparse, then the program () completely recovers \(x\).
That is, a noiseless linear transformation of a sparse vector is completely recovered by a \(\ell_1\)-minization program with an overwhelming probability, if
%
\Disp{
\delta_{S} +\delta_{2S} +\delta_{3S} <1
}
%
}

\Result
{Definition}
{
Let \(A\) be an \(n \times p\) matrix, with
%
\Disp{
\delta_{S} +\delta_{2S} +\delta_{3S} <1
}
%

having unit \(\ell_2\)-norm columns.
For each integer \(S \in \MB{N}\), we say that \(A\) satisfies the RIP of order \(S\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq S\), for all \(T\) with \(|T| \leq S\),
%
\Disp{
(1-\delta_S) \|x\|^2
\leq \|A_T x\|_2^2
\leq (1+\delta_S) \|x\|^2
}
%
}

@@

Moreover, for \(T,T' \subset \{1, \dotsc, p \}\), let \(\vartheta_{S,S'}\) be the smallest constant such that
%
\Disp{
| \IP{ X_T c, X_{T'} c' } |
\leq \vartheta_{S,S'} \cdot \| c \|_2 \|c'\|_2
}
%

For concreteness, consider a linear transformation with noise,
%
\Disp{
y =Ax +z
}
%
where \(z\) is an i.i.d., zero-mean, \(\sigma\)-variance AWGN vector.
How can we hope to estimate \(h\) when, in addition to insufficient observations, there are too few observations?

\Result
{Program}
{
Let \(A,y\) be given.
Find \(x\) with
%
\Disp{
\min_{x' \in \MB{K}^p}  \|\hat{x'}\|_1 \\ \NT
\RM{subject}\; \RM{to} \quad \|A^\H r\|_\infty \leq \lambda_p \sigma
}
%
where \(r =y -A \hat{x}\).
}
And it can be shown that this \(\ell_\infty\)-constraint problem may be recast as a linear program.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(A \in \MB{V}_\MB{K}(M \cdot N)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{M}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
%
\Disp{
   \MB{P}( |\|Ax\|_2^2 -\|x\|_2^2| \geq \epsilon \|x\|_2^2)
   \leq 2 \exp (-n c_0(\epsilon))
}
%
where we have
%
\Disp{
c_0(\epsilon)
=\epsilon^2/4 -\epsilon^3/6.
}
%
}

@@

To explain the idea, consider a simplified scenario.
Let \(x[t] \in \MB{R}^N\) be random instances of i.i.d.\ Rademacher distribution.
Consider a linear time-invariant channel with
%
\Disp{
y[t] =(x[t] \star h[t]) +z[t]
}
%
where \(h[t] \in \MB{R}^L\) is the channel's impulse response, \(x[t] \in \MB{R}^N\) as the input, \(y[t] \in \MB{R}^N\) as the output, and \(z[t] \in \MB{R}^L\) are random instances of i.i.d.\ normalized AWGN, and \(N \gg L\).
Here, if the convolutional relation is expressed by a matrix \(X\), \(X\) is a Toeplitz matrix, so that
%
\Disp{
y =X h
}
%
where \(X\) takes the form
%
\Disp{
X
=\begin{bmatrix}
x_1, &0, &\cdots, &0 \\
x_2, &x_1, &\cdots, &0 \\
\vdots, &\vdots, &\ddots, &0 \\
x_N, &x_{N-1}, &\cdots, &x_1
\end{bmatrix}
}
%
We seek to get \(h\) in this undertermined system.

@@

The setting here is \(y =Ax\), the noiseless, real-number case.
Same as before, let \(y \in \MB{V}_\MB{K}(M)\), \(x \in \MB{V}_\MB{K}(N)\) which is \(s\)-sparse, while \(M \ll N\).
We pick up the columns of \(A\) greedily, hoping to correspond to the support of \(x\).

@@

\Result
{Theorem}
{
   Following the setting described above, suppose, for \(0 <\delta <1\),
%
\Disp{
   M \geq 16s \log (N/\delta)
}
%
Then Algorithm () recovers \(x\) completely, with overwhelming probability \(1-\delta\).
}

@@

It is interesting to note that, ever since, the direct application of \(\ell_1\)-problem following the orignal Cand\`es-and-Tao approach has been seemingly rare.
Scholars has applied OMP in favor of DS, in the ease of implementation of the former, and OMP becomes perhaps the most widely used channel estimation technique.
To see this, let \(\M{F}\) be the precoder and \(\M{W}\) the combiner, and \(\M{H}\) the channel, and consider the noiseless case.
Let signal \(x\) be sent, and \(y\) be receiverd, that is
%
\Disp{
   \V{y} =\M{W} \M{H} \M{F} \V{x}
}
%

\Result
{Definition}
{
Define \(\RM{vec}(\M{A}) \in \MB{K}^{nm}\) to be the vectorization of \(\M{A} \in \MB{M}_{\MB{K}}(n,m)\).
}

\Result
{Definition.}
{
For \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\) and \(\RM{vec}(A) \in \MB{M}_{\MB{K}}(n,m)\)
Define the Kronecker product \(\RM{vec}(A) \in \MB{K}^{nm}\) 
}

With (), scholars often exploit the relation
%
\Disp{
\RM{vec}(Y)
=\big[ (F^\H) \otimes W \big] \RM{vec}(\M{H})
}
%

@@

\subsection{Further Development on Compressive Channel Sensing}

The literature on Compressive Channel Sensing has since been vast, and we need not and cannot go through all of them here.
Rather, we analyze the respective contribution and weakness on some of the recent seminal papers.

@@
